\bf A simple algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
more

\begin{proof}
Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
either of $g_1$ and $g_2$ is a separable sum of
the indicator function of a convex set, whose prox is simply the
euclidean projection onto the set,  and a linear transformation $z
\mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one
computes their respective proximal operators $\prox_{\tau g_1} :
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1}$, $\prox_{\sigma g_2}: \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$
$\prox_{\lambda g_1}(y, p) = ((y)_+, p - \lambda e_1)$ and $\prox_{\lambda
  g_2}(x, q) = ((x)_+, q - \lambda e_2)$. Algorithm \ref{Tab:algo} is
then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP \eqref{eq:unconstrained_pb}
 with the choice of parameters: $\sigma = 1 \in (0, 1]$, $\sigma_x =
         \sigma_y = 0 \in [0, \sigma)$,
 $\lambda_{xy} := \frac{\sqrt{(\sigma^2 - \sigma_x^2)(\sigma^2 -
               \sigma_y^2)}}{\sigma L_{xy}} = \sigma / \|K\| =
           1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
           \lambda_{xy}]$. The convergence result then follows from
         \cite[Theorem 4.2]{he2013accelerating}.
\end{proof}
\subsection{Practical considerations: Efficient computation of $Ay$ and $A^Tx$.}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.

@@

One notes that $(F \otimes B)^T = F^T \otimes B^T$.
$F \otimes B$ can be very much larger than both $F$ and $B$ in dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and $B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a $10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in \mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$ without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1, ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of $s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one easily verfies that $Y$ is the matrix product of the ``small'' matrices $B$, $X$, and $F^T$, i.e
\begin{equation}
  \label{eq:kron_matvec}
  Y = BXF^T
\end{equation}

@@

>>>>

\begin{proof}
Note that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$ clearly satisfies
assumptions B.1, B.2, B.3, B.5, and B.6 of \cite{he2013accelerating}
with $L_{xx} = L_{yy} = 0$ and $L_{xy} = L_{yx} = \|K\|$. Now,
either of $g_1$ and $g_2$ is a separable sum of
the indicator function of a convex set, whose prox is simply the
euclidean projection onto the set,  and a linear transformation $z
\mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one
computes their respective proximal operators $\prox_{\tau g_1} :
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1}$, $\prox_{\sigma g_2}: \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$
$\prox_{\lambda g_1}(y, p) = ((y)_+, p - \lambda e_1)$ and $\prox_{\lambda
  g_2}(x, q) = ((x)_+, q - \lambda e_2)$. Algorithm \ref{Tab:algo} is
then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP \eqref{eq:unconstrained_pb}
 with the choice of parameters: $\sigma = 1 \in (0, 1]$, $\sigma_x =
         \sigma_y = 0 \in [0, \sigma)$,
 $\lambda_{xy} := \frac{\sqrt{(\sigma^2 - \sigma_x^2)(\sigma^2 -
               \sigma_y^2)}}{\sigma L_{xy}} = \sigma / \|K\| =
           1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
           \lambda_{xy}]$. The convergence result then follows from
         \cite[Theorem 4.2]{he2013accelerating}.
\end{proof}
\subsection{Practical considerations}
\paragraph{\textbf{Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo} most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop}-type Poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}.

@@

One notes that $(F \otimes B)^T = F^T \otimes B^T$.
$F \otimes B$ can be very much larger than both $F$ and $B$ in
dimensions. For example, if $r = n = r = s = 1000$, so that $F$ and
$B$ are $10^3$-by-$10^3$ matrices, then $F \otimes B$ is a
$10^6$-by-$10^6$ matrix! Fortunately, given a vector $x \in
\mathbb{R}^{rs}$ one can compute the matvec product $(F \otimes B)x$
without forming $F \otimes B$. Indeed, let $y := (F \otimes B)x$. We
rewrite the row vector $x$ as an $s$-by-$r$ matrix $X = [X_0, X_1,
  ..., X_{r-1}]$, where each column vector $X_i$ is the $i$th block of
$s$ elements of $x$ read from left to right. Similarly, rewrite $y$ as
as an $n$-by-$m$ matrix $Y = [Y_0, Y_1, ..., Y_{m-1}]$. Then one
easily verfies that $Y$ is the matrix product of the ``small''
matrices $B$, $X$, and $F^T$, i.e

\begin{equation}
  \label{eq:kron_matvec}
  Y = BXF^T
\end{equation}

@@

\paragraph{\textbf{Computing $\|K\|$.}} Power iteration (Perron-Frobenius)...
